%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.3in,top=0.3in,right=0.3in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Samuel Path} % Your name
\address{119 Cours Lafayette, 69006 Lyon, France} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{+33 6 61 36 93 49 | samuel.path@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}
%--copy and paste this region  if you need more--
{\bf SHOPIFY}{, Senior Software Engineer} \hfill {\em Sep 2022 - Today}\\
Full-stack software development using Ruby on Rails and React.js.

Working in the payments team, maintaining existing payment methods (Stripe, PayPal, Apple Pay, etc.), assimilating new payment methods, and extending the offering of payment methods provided to 300+ million shoppers worldwide.

Shipped features that have already added millions of dollars in yearly GPV (Gross Payments Volume), some of them partly of my own initiative during internal hackathons.

Working on systems that need to handle billions of dollars of transactions every year, with some peak loads during Black Friday or flash sales for key customers like Supreme.\\

{\bf EDF}{, Senior Software Engineer} \hfill {\em Dec 2021 - Aug 2022 · 9 mos}\\
Full-stack software development using Ruby on Rails and Angular.

Worked on a key strategic initiative for the purchasing department handling billions in purchases every year (ranging from contracts with IT companies to materials to build nuclear plants). Its goal was to build a centralized cockpit where the key stakeholders could have a live view of all purchases throughout their entire lifecycles.

The project was initially built by a team that didn't deliver in terms of quality and deadlines. I was then called with a team of experts to "save" the project by introducing state of the art quality standards. We were able to deliver on time and on budget.

Some high-ranking key stakeholders considered me as a MVP on this project, with one calling me "the best software engineer I've had the chance to work with".\\

{\bf ADENES}{, Senior Software Engineer} \hfill {\em Oct 2020 - Nov 2021 · 1 yr 2 mos}\\
Full-stack development on various software products for the insurance industry, using C\# and Angular.

Worked directly under the company's CIO to work on key strategic projects. 2 examples:

- Some complex notification workflows (to send emails or SMS to disaster victims) had business logics all over the codebase. Because of that, the slightest update would often require days or even weeks of work instead of hours. I was able to extract all the logics in a centralized place, and add extensive documentation. Upon leaving, software engineers were able to make changes in a few keystrokes that used to take a lot of unproductive toil.

- The company's leaders aimed at nudging the insured customers to use an online tool (both on web and mobile) to book an expert's visit, instead of calling their call center. Each call was costly, while the marginal cost of an online booking was basically free. Before I joined, a lot of effort was made but still only around 10\% of customers used the online tool. After extensive data analysis and a lot of poking, I was able to increase that number to 40\%, thus allowing the company to save a lot of money all the while improving customer satisfaction.\\

{\bf CATHOLIC UNIVERSITY OF LYON}{, Part-Time Teacher} \hfill {\em Sep 2020 - Feb 2021 · 6 mos}\\
Teaching advanced web programming, with a focus on advanced JavaScript patterns and React.js.\\

{\bf ESKER} \hfill {\em Aug 2014 - Feb 2021 · 6 yrs 3 mos}\\
• {\bf Software Integration Consultant} \hfill {\em Sep 2020 - Feb 2021 · 6 mos}\\
At R\&D, I used to work on building and maintaining the core product. As a consultant, I customized the core product to custom design it for the customers using the JavaScript API maintained by R\&D. I mainly focused on building middlewares to make sure the Esker SaaS inputs/outputs communicated correctly with the customers' various ERP's. This involved a lot of data heavy transformation, from and into various formats over multiple channels.

In regular direct contact with high-ranking employees from Fortune 500 companies. Upon leaving, a few of them told me how disappointed they were to lose our partnership.

• {\bf Software Engineer} \hfill {\em Jan 2017 - Oct 2017 · 10 mos}\\
Full-stack software development using C\#, Ionic and Angular.

Part of a team of 8 developers (working in collaboration with a R\&D of 100+ developers) working on a Sales Order Processing B2B SaaS application (web + mobile), allowing our customers to automate time-intensive and error-prone tasks.

• {\bf Scrum Master} \hfill {\em Jan 2016 - Dec 2016 · 1 yr}\\
Turned my focus from serving customers to serving engineers, leading them in continuous improvement, making sure they were fulfilled and had everything they needed to be productive, setting relevant KPIs and keeping track of them using Salesforce, helping teams from various services to better collaborate.

Under my service, we were able to divide the average final response time by 3, all the while increasing customer satisfaction and employees retention.

• {\bf International Technical Support Engineer} \hfill {\em Aug 2014 - Dec 2015 · 1 yr}\\
Esker is a special SaaS company in that it only hires engineers in their support teams, leading to world-class support quality. Support engineers are not considered second-class employees, and are provided with a higher entry-level total compensation than software engineers.

Provided support to SaaS B2B large account customers worldwide (in English, French and German), turning crises into opportunities, and solving technical issues, mainly related to JavaScript and cloud infrastructures. Worked closely with R\&D on complex debugging sessions.\\

{\bf SNCF}{, Software Engineer} \hfill {\em Feb 2014 - Jun 2014 · 5 mos}\\
Sole developer in a team of 4 project managers, building custom tools using Python to automate time-intensive tasks. Also took the initiative to write extensive documentation, allowing them to update the tools themselves (which they were able to do, years later).

A project manager told me that my few months in their team had a deep impact on their productivity. In his specific case, he was then able to do in a few minutes what would otherwise take him hours of painful toil.\\

{\bf ATOS WORLDLINE GLOBAL}{, Software Engineer} \hfill {\em May 2012 - Sep 2012 · 5 mos}\\
Developed highly secured web services in Java for BNP Paribas (one of Europe's leading banks).\\

{\bf AKUITEO}{, Software Engineer} \hfill {\em May 2011 - Aug 2011 · 4 mos}\\
I developed various features for an ERP, using Java.\\

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
%--copy and paste this region  if you need more--
{\bf INSA LYON}, Master of Science (M.Sc.), Computer Science \hfill {\em Sep 2008 - Jun 2014} 
\\ Wide overview of programming languages, methodologies \& techniques.
\\ One of the most prestigious engineering degrees in France {\em (its average student finished high school with a grade of 17,9/20 while other prestigious schools like CentraleSupélec have an average of 17,67/20, only the Ecole Polytechnique does better with an average of 17,93/20)}.
\\
%--copy and paste this region  if you need more--

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills \& Interests}
• {\bf Languages}: French (native), English (fully bilingual, TOEIC 990/990), German\\
• {\bf Interests}: Literature, long distance \& trail running, engaging with the wider tech community (10k followers on Twitter), community development among disadvantaged minorities \& humanitarian aid work (3 gap years cumulated in 12 countries before and during my studies)
\end{rSection}

\end{document}----------------------------
